### 2020-06-02 report/sections/server/codegen/testing.tex
Report: make wording more consistent

As the generated TypeScript code makes assumptions about the
environment in which it is used (for example, having the \texttt{ws}
WebSocket package installed on server-side targets), we require a
sandbox environment to type-check the generated code. 
The sandbox contains the minimal boilerplate required
for testing -- this involves having the WebSocket package installed
for server-side targets, the React.js framework (\cref{section:react})
instantiated for browser-side targets,
and corresponding \texttt{tsconfig.json} files for both targets to
be picked up by the TypeScript Compiler.

>>>>

As the generated TypeScript code makes assumptions about the
environment in which it is used (for example, having the \texttt{ws}
WebSocket package installed on server-side endpoints), we require a
sandbox environment to type-check the generated code. 
The sandbox contains the minimal boilerplate required
for testing -- this involves having the WebSocket package installed
for server-side endpoints, the React.js framework (\cref{section:react})
instantiated for browser-side endpoints,
and corresponding \texttt{tsconfig.json} files for both targets to
be picked up by the TypeScript Compiler.

### 2020-06-02 report/sections/server/codegen/workflow.tex
Report: make wording more consistent

Formally, API generation is a function of the constructed
\texttt{Endpoint} instance
\textit{and} the target specified in the command line. We use a 
different code generation strategy for implementations running on
the servre (\cref{chap:node}) versus the browser (\cref{chap:react}).
In this subsection, we explain how we perform API generation
at a higher level of abstraction.

>>>>

Formally, API generation is a function of the constructed
\texttt{Endpoint} instance
\textit{and} the target specified in the command line. We use a 
different code generation strategy for implementations running on
the server (\cref{chap:node}) versus the browser (\cref{chap:react}),
hereafter referred to as \textit{server-side endpoints} and 
\textit{browser-side endpoints} respectively.
In this subsection, we explain how we perform API generation
at a higher level of abstraction.
